The \dealii Library, Version 9.6

### 2024-09-14 9.6/paper.tex
ACCESS

\todo[inline]{Did anyone actually use TACC resources? Timo or Marc? If
not, we need to delete the following sentence.}

@@

\todo[inline]{Marc: Update the following to ACCESS, see https://access-ci.org/about/acknowledging-access/}

>>>>

@@

\todo[inline]{Marc: please insert allocation}

This work used [resource-name] at [resource provider] through allocation [allocation number] from the Advanced Cyberinfrastructure Coordination Ecosystem: Services \& Support (ACCESS) program, which is supported by National Science Foundation grants \#2138259, \#2138286, \#2138307, \#2137603, and \#2138296. See \cite{Boerner2023}.
